Clique and Constraint Models for Maximum Common (Connected) Subgraph Problems

### 2016-04-15 paper/paper.tex
Refcheck, temporarily
Rewrap text

@@

In some applications, nodes and edges are associated with labels. We note $\lambda(u)$ and $\lambda(\{u,v\})$ the label of a node $u$ and an edge $\{u,v\}$, respectively. In this case, the common  subgraph must match components the labels of which are compatible, and we note $\simeq$ the compatibility relationship, {\em i.e.}, labels $\lambda_1$ and $\lambda_2$ are compatible if $\lambda_1\simeq\lambda_2$. This kind of label compatibility constraint is handled in a straightforward way in both CP and clique-based approaches:
\begin{itemize}
\item For CP, we restrict the domain of every variable $x_u$ to nodes with compatible labels, {\em i.e.}, $\forall u\in N_G, D(x_u) = \{\bot\}\cup \{u'\in N_{G'}, \lambda(u)\simeq\lambda(u')\}$. We also have to ensure that edge labels are preserved in edge constraints, {\em i.e.}, $\forall \{u,v\}\subseteq N_G, (x_u=\bot)\vee (x_v=\bot) \vee ((\{u,v\}\in E_G\Leftrightarrow \{x_u,x_v\}\in E_{G'}) \wedge (\lambda(\{u,v\}) \simeq \lambda(\{x_u,x_v\})))$.

\item For clique-based approaches, label compatibility is handled through the definition of the association graph, by restricting the set of matching nodes to pairs of nodes with compatible labels, {\em i.e.}, $N_{G_C} = \{(u,u')\in N_G\times N_{G'}, \lambda(u)\simeq\lambda(u')\}$. Also, edges of the association graph are restricted to pairs $\{(u,u'),(v,v')\}$ such that $\lambda(\{u,v\}) \simeq \lambda(\{u',v')\}$.
\end{itemize} 
Labels usually simplify the solution process, both for CP and clique-based approaches: Node labels reduce domain sizes for CP, and the number of matching nodes in the association graphs; Edge labels tighten edge constraints for CP, and make the association graph sparser for clique-based approaches.

@@

\FloatBarrier
\bibliographystyle{splncs}
\bibliography{paper}

>>>>

\usepackage{refcheck}

\makeatletter\@ifpackageloaded{refcheck}{\newcommand{\citesforrefcheck}{\nocite{*}}}{\newcommand{\citesforrefcheck}{}}\makeatother

@@

In some applications, nodes and edges are associated with labels. We note $\lambda(u)$ and
$\lambda(\{u,v\})$ the label of a node $u$ and an edge $\{u,v\}$, respectively. In this case, the
common  subgraph must match components the labels of which are compatible, and we note $\simeq$ the
compatibility relationship, {\em i.e.}, labels $\lambda_1$ and $\lambda_2$ are compatible if
$\lambda_1\simeq\lambda_2$. This kind of label compatibility constraint is handled in a
straightforward way in both CP and clique-based approaches:

\begin{itemize}
\item For CP, we restrict the domain of every variable $x_u$ to nodes with compatible labels, {\em
    i.e.}, $\forall u\in N_G, D(x_u) = \{\bot\}\cup \{u'\in N_{G'}, \lambda(u)\simeq\lambda(u')\}$.
    We also have to ensure that edge labels are preserved in edge constraints, {\em i.e.}, $\forall
    \{u,v\}\subseteq N_G, (x_u=\bot)\vee (x_v=\bot) \vee ((\{u,v\}\in E_G\Leftrightarrow
    \{x_u,x_v\}\in E_{G'}) \wedge (\lambda(\{u,v\}) \simeq \lambda(\{x_u,x_v\})))$.

\item For clique-based approaches, label compatibility is handled through the definition of the
    association graph, by restricting the set of matching nodes to pairs of nodes with compatible
    labels, {\em i.e.}, $N_{G_C} = \{(u,u')\in N_G\times N_{G'}, \lambda(u)\simeq\lambda(u')\}$.
    Also, edges of the association graph are restricted to pairs $\{(u,u'),(v,v')\}$ such that
    $\lambda(\{u,v\}) \simeq \lambda(\{u',v')\}$.
\end{itemize}

Labels usually simplify the solution process, both for CP and clique-based approaches: Node labels
reduce domain sizes for CP, and the number of matching nodes in the association graphs; Edge labels
tighten edge constraints for CP, and make the association graph sparser for clique-based approaches.

@@

\citesforrefcheck

\bibliographystyle{splncs}
\bibliography{paper}
